Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
clarification of this initial state thingy

{\em The first approach} uses a {\em naive}
technique that starts by devising a digital controller that stabilizes the system
whilst remaining safe for a 
pre-selected time horizon; then, it verifies its potential safety by unfolding
the dynamics of the system and checking for a {\em completeness threshold}, i.e.,
the number of iterations required to sufficiently unwind
the closed-loop state-space system such
that the boundaries are not violated for any larger number of iterations.
As it requires explicit unfolding up to the completeness
threshold, this approach may suffer from state space explosion.

>>>>

{\em The first approach} uses a {\em naive}
technique that starts by devising a digital controller that stabilizes the system
whilst remaining safe for a 
pre-selected time horizon and a single initial state; then, it verifies its potential safety by unfolding
the dynamics of the system, considering the full hyper-cube of initial states, and checking for a {\em completeness threshold}, i.e.,
the number of iterations required to sufficiently unwind
the closed-loop state-space system such
that the boundaries are not violated for any larger number of iterations.
As it requires explicit unfolding up to the completeness
threshold, this approach may suffer from state space explosion.
